Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-07 paper.tex
Comment on scheduling
some more text

        Many neuroimaging workflow engines currently exist. Examples include
        Nipype, Pipeline System for Octave and Matlab (PSOM), LONI, SPM, FastR,
        Automated Analysis (AA) and Pydpiper\note{add citations here}. These 
        workflow engines aim to satisfy four criteria: 1) straightforward \tristan{easy? facilitated?} 
        workflow composition, 2) performance, 3) portability of the workflows 
        and 4) reproducibility of the analyses. While these workflow engines
        do tackle performance, it is mainly limited to minimizing computation
        time and does not consider data transfer times -- which are typically
        costly in Big Data settings. Therefore, these engines need to be adapted
        for the processing of neuroimaging data.

@@

        \section{Workflow sharing}\label{sharing}

@@

                Writting BigData to Lustre is very costly compared to local 
                node storage. BigData filesystems like HDFS may not necessarily
                be the best solution for HPC as they will not only use up 
                storage on compute nodes, but also replicate the data across 
                the cluster taking up a significant amount of storage space.
                Moreover, while BigData frameworks typically execute on a 
                dedicated BigData cluster, they will be on a shared cluster in
                HPC, with many processed trying to access the memory. The 
                following are two optimizations made for  \note{two or one}

                Alluxio, formerly known as Tachyon, is an in-memory filesystem
                that stores lineage data to offset the cost of writing data to 
                disk. The assumption that Alluxio makes is that it will be less
                costly to recompute the data that to store the data to disk and
                replicate across the network for fault tolerance. However,
                unlike Spark applications, Alluxio is meant to run indefinitely
                , making it unfavourable, in some cases, to recompute the data
                from its starting point. For this, Alluxio evaluates the 
                lineage data and selects the

                Triple-H leverages the heterogeneity of HPC clusters to 
                optimize the data's placement across the cluster for most 
                efficient use. It has two modes, default and Lustre integrated,
                that allows it to execute on systems with and without access
                to a distributed filesystem.

            \note{scientific: shared FS such as Lustre, NFS, S3
            big data: mapreduce - HDFS, spark and dask shared or distributed}
        \section{BigData Scheduling}\label{sched}

>>>>

        Many neuroimaging workflow engines currently exist. Examples include
        Nipype, Pipeline System for Octave and Matlab (PSOM), LONI, SPM, FastR,
        Automatic Analysis (AA) and Pydpiper\note{add citations here}. These 
        workflow engines aim to satisfy four criteria: 1) straightforward \tristan{easy? facilitated?} 
        workflow composition, 2) performance, 3) portability of the workflows 
        and 4) reproducibility of the analyses. While these workflow engines
        do tackle performance, it is mainly limited to minimizing computation
        time and does not consider data transfer times -- which are typically
        costly in Big Data settings. Therefore, these engines need to be adapted
        for the processing of neuroimaging data.

@@

@@

                Writting BigData to Lustre is very costly compared to local 
                node storage. Distributed filesystems found on HPC 
                infrastructure provide their own form of fault-tolerance, 
                therefore, adding a BigData filesystem such as HDFS which 
                replicates the data may burden the storage layer only to 
                providea feature which already exist. This is especially 
                problematic as storage on HPC compute nodes may be limited.
                Moreover, while BigData frameworks typically execute on a 
                dedicated BigData cluster, they will be on a shared cluster in
                HPC, with many processed trying to access the memory. The 
                following are two optimizations made for the storing of BigData
                .

                Alluxio, formerly known as Tachyon, is an in-memory filesystem
                that stores lineage data to offset the cost of writing data to 
                disk. The assumption that Alluxio makes is that it will be less
                costly to recompute the data that to store the data to disk and
                replicate across the network for fault tolerance. However,
                unlike Spark applications, Alluxio is meant to run indefinitely
                , making it unfavourable, in some cases, to recompute the data
                from its starting point. For this, Alluxio evaluates the 
                lineage data and checkpoints the files which have been 
                repeatedly accessed (i.e. hot files). This strategy also helps 
                in avoiding the checkpointing of intermediary files.

                Triple-H leverages the heterogeneity of HPC clusters to 
                optimize the data's placement across the cluster for most 
                efficient use. It aims to reduce the I/O bottleneck of writing 
                through data buffering and caching. Triple-H has two modes of
                operation, Default and Lustre integrated,
                that allows it to execute on systems both with and without 
                access to a distributed filesystem. To further reduce I/O in
                HPC systems, Triple-H leverage's Lustre's fault tolerance 
                instead of using HDFS's replication-based fault-tolerance. 
                Triple-H improves 
                performance of cluster I/O by writing the data to
                the most optimal storage layer (RAMDisk, SSD, HDD, Lustre) 
                dictacted by the selected placement policy (i.e. Greedy or 
                Load-balanced).

                Although both of these solutions have shown to improve I/O
                performance

        \section{BigData Scheduling}\label{sched}
